Collaborative Test-Driven Scientific Model Validation

### 2013-11-23 sciunit-icse14/sciunit-icse14.tex
Started describing unit testing

Code review is reasonably effective \cite{creffectiveness1,creffectiveness2}. However, to be most effective reviewers must expend considerable effort \cite{effort}, and code review is most effective for resolving  issues related to software architecture \cite{evolvability}. 
For these reasons, most software development teams supplement code reviews with a number of more {automated} approaches to verification and validation. One of the most widely-adopted approaches is \emph{unit testing}.

>>>>

Code review is reasonably effective \cite{creffectiveness1,creffectiveness2}. However, to be most effective reviewers must expend considerable effort \cite{effort}, and code review is most effective for resolving  issues related to software architecture \cite{evolvability}. 
For these reasons, most software development teams supplement code reviews with a number of more {automated} approaches to verification and validation. One of the most widely-adopted approaches is \emph{unit testing}. In brief, unit tests are functions that check a single component of a program against a single well-defined correctness criterion. A suite of such tests can be seen as a partial specification of a program or component.  Test suites complement code review procedures in several ways:
\begin{enumerate}
\item They help ensure that a code modification does not cause a \emph{regression} in another part of a program.
\item They help measure development progress. Developers can use a test suite to determine which functionality is not yet adequately implemented.
\item They serve as a form of documentation. By inspecting the test suite itself, a developer can see which modes of usage the development team collectively considers most important.
\end{enumerate}
